User-level Grid Monitoring with Inca 2

### 2007-02-27 papers/hpdc-gmw-2007/paper.tex
just suggestions
git-svn-id: file:///localdisk/subversion/inca/trunk/pubs@6586 7dba3f4a-8be6-0310-8b3b-b4fec25ea7f3

% Standard "Grids are good" intro paragraph.  But are complex.  
Grid systems provide unified and coherent access to distributed computing,
data storage and analysis, instruments, and other resources.  These systems
require the careful coordination of software packages, services, and
configurations across multiple, heterogeneous resources.  The TeraGrid
project~\cite{teragrid}, for example, manages the coordination of software and
services by deploying and monitoring a common user environment across
distributed, heterogeneous resources. The organization of TeraGrid software
and services is referred to as the Coordinated TeraGrid Software and Services
(CTSS).  TeraGrid's software and services uniformity simplifies access to its
resources, which consist of more than 102 teraflops of compute capability and
more than 15 petabytes of online storage, all interconnected by a network that
can transfer a terabyte of data in under 10 minutes.

% Complex means they are difficult to provide and maintain. Describe the
% stakeholders.   Monitoring is needed.
Providing and maintaining a stable infrastructure for these complex 
Grid systems poses challenges for both administrators who build and
maintain Grid resources and scientists who use them.  First, system
administration is distributed across multiple administrative domains 
requiring a significant amount of coordination.  This is typically performed by
a group of Grid administrators or operators who consider local site policies and
resource heterogeneity
and decide when software (including updates and patches) should be deployed to
resources and how it should be configured.  
Each site's system administrators, who are not necessarily Grid
experts, are then responsible for providing the required Grid software
components and services for their resource and debugging any problems that
arise.  Well-defined requirements and good communication are required in this
model.  Otherwise, inconsistencies between the resources arise that either
inconvenience the user or prevent them from using a particular resource
altogether.  A second challenge is that failures will occur over
time in the Grid services due to network or system failures, software
misconfiguration, or software bugs.  In order to address these challenges,
Grid monitoring can be used to detect such problems, leading to a more
stable and dependable Grid infrastructure.

@@

\item In order to reflect regular user experiences, tests or performance
measurements of the Grid infrastructure should be done from a standard user
account.  It is important not to execute from a system administrator's account,
since it may have special privileges and use custom shell initialization files.

@@

\item User-level tests and performance measurements should be written and
maintained within an iterative refinement process.  An iterative process is
required since Grids are dynamic and software environments change over time as
packages are upgraded.  It is also difficult to write and deploy a test
correctly the first time because of portability issues and incomplete user
documentation.  For example, it may take some iterations to determine whether a
detected failure is the result of a faulty test, user document, or Grid
resource.

@@

% Incat is interface Inca admin uses to configure reporters to resources
% introduce series here; why suites are important It is designed to make the
% effort of configuring and maintaining 100s series on resources easilty
The Inca administrative tool (incat) is a GUI implemented in Java Swing that an
Inca administrator uses to configure user-level Grid monitoring on their
resources.  Incat allows an Inca administrator to choose which resources to
monitor and which reporters to deploy to those resources.  The configuration
is stored in a XML file and sent to the agent, which handles the implementation
(as described in the next section).  The Inca administrator can reload the
configuration at any point and make updates.  Incat provides a number of
conveniences that enable a large number of results to be managed and collected
with a minimum effort.

@@

% Resource information organized to make it easier to maintain
For each monitored resource, an Inca administrator selects an access method
(SSH or Globus) to access the resource and start monitoring there (described
in Sections~\ref{agent} and ~\ref{rm}).  Resources can also be grouped
together and referenced in the series configuration.  This facilitates the
process of executing the same series on multiple resources.  Furthermore,
attributes called \emph{macros} can be attached to resource groups for
reference in series configuration (i.e., inputs
and runtime environment).  For example, it is useful to have a macro called
'jobmanager' since the batch system is likely to differ from one machine to
the next and multiple tests will require its value.  A resource macro can also
have multiple values in which case the series will be executed on the resource
once for each macro value.  The
benefit of resource groups and macros is that when a reporter is executed on a
resource multiple times with different input arguments, it can be represented
succinctly.  Similarly, when a resource attribute is changed it only has to be
changed in one place for every series that references it to be updated.
Initial Inca configuration and maintenance is therefore easier and less error prone.

@@

To further manage the Inca deployment, the agent regularly pings the reporter
managers on each resource in order to detect when a reporter manager has
failed so it can be restarted.  For example, if a resource goes down for a
planned maintenance, the agent will attempt to restart the reporter manager
(by default every hour) until it succeeds.  The agent also maintains a local
cache of reporters and their dependencies; it periodically checks the
repositories for updates (every 4 hours by default) and automatically
distributes them to the reporter managers if the latest version is desired.  
The agent is implemented in Java.

@@

The reporter manager is implemented in Perl since Perl is available by default
on UNIX machines.  The cron scheduling is implemented using the CPAN Perl
module Schedule::Cron.

@@

The Inca depot server is responsible for storing configuration information and
the data produced by reporters. The depot uses a relational database via
Hibernate~\cite{hibernate} so that it can use a variety of databases.  The
depot provides full archiving of reporter output and structures its schema
around series and the minimization of redundant data, i.e., only stores
changes from one report to another in a report series.  The depot also
supports comparisons that are executed on a newly received report; 
% need Jim's help with this sentence
currently regular expression matching and greater than/less than comparisons are 
supported.  Optionally, an Inca administrator can select to receive
email notification when the result of the comparison changes.

Data can be queried using SQL queries. Predefined queries exist to return the
latest report instances of a suite, a single report instance, or a report
history.  A Web services interface is also available to provide
unauthenticated query access to data.  The depot is implemented in Java.

>>>>

% Standard "Grids are good" intro paragraph.  But are complex.  
Grid systems provide unified and coherent access to distributed computing,
data storage and analysis, instruments, and other resources.  These systems
require the careful coordination of software packages, services, and
configurations across multiple, potentially heterogeneous, resources.  The TeraGrid
project~\cite{teragrid}, for example, manages the coordination of software and
services by deploying and monitoring a common user environment across
distributed, heterogeneous resources. The organization of TeraGrid software
and services is referred to as the Coordinated TeraGrid Software and Services
(CTSS).  TeraGrid's software and services uniformity simplifies access to its
resources, which consist of more than 102 teraflops of compute capability and
more than 15 petabytes of online storage, all interconnected by a network that
can transfer a terabyte of data in under 10 minutes.

% Complex means they are difficult to provide and maintain. Describe the
% stakeholders.   Monitoring is needed.
Providing and maintaining a stable infrastructure for these complex 
Grid systems poses challenges for both administrators who build and
maintain Grid resources and scientists who use them.  First, system
administration is distributed across multiple administrative domains 
requiring a significant amount of coordination.  This is typically performed by
a group of Grid administrators or operators who consider local site policies and
resource heterogeneity
and decide when software (including updates and patches) should be deployed to
resources and how it should be configured.  
Each site's system administrators, who are not necessarily Grid
experts, are then responsible for providing the required Grid software
components and services for their resource and debugging any problems that
arise.  Well-defined requirements and good communication are required in this
model.  Otherwise, inconsistencies between the resources arise that either
inconvenience the user or prevent them from using a particular resource
altogether.  A second challenge is that failures will occur over
time in the Grid services due to network or system failures, software
misconfiguration, or software bugs. 
Grid monitoring can be used to detect such problems, leading to a more
stable and dependable Grid infrastructure.

@@

\item In order to reflect regular user experiences, tests or performance
measurements of the Grid infrastructure should be done from a standard user
account.  It is important not to execute from a system administrator's account,
because it may have special privileges and use custom shell initialization files.

@@

\item User-level tests and performance measurements should be written and
maintained within an iterative refinement process.  An iterative process is
required because Grids are dynamic and software environments change over time as
packages are upgraded.  It is also difficult to write and deploy a test
correctly the first time because of portability issues and incomplete user
documentation.  For example, it may take some iterations to determine whether a
detected failure is the result of a faulty test, user document, or Grid
resource.

@@

% Incat is interface Inca admin uses to configure reporters to resources
% introduce series here; why suites are important It is designed to make the
% effort of configuring and maintaining 100s series on resources easilty
The Inca administrative tool (incat) is a GUI, implemented using Java Swing, which an
Inca administrator uses to configure user-level Grid monitoring on their
resources.  Incat allows an Inca administrator to choose which resources to
monitor and which reporters to deploy to those resources.  The configuration
is stored in a XML file and sent to the agent, which handles the implementation
(as described in the next section).  The Inca administrator can reload the
configuration at any point and make updates.  Incat provides a number of
conveniences that enable a large number of results to be managed and collected
with a minimum effort.

@@

% Resource information organized to make it easier to maintain
For each monitored resource, an Inca administrator selects an access method
(SSH or Globus) to access the resource and start monitoring there (described
in Sections~\ref{agent} and ~\ref{rm}).  Resources can also be grouped
together and referenced in the series configuration.  This facilitates the
process of executing the same series on multiple resources.  Furthermore,
attributes called \emph{macros} can be attached to resource groups for
reference in series configuration (i.e., inputs
and runtime environment).  For example, it is useful to have a macro called
'jobmanager' because the batch system is likely to differ from one machine to
the next and multiple tests will require its value.  A resource macro can also
have multiple values in which case the series will be executed on the resource
once for each macro value.  The
benefit of resource groups and macros is that when a reporter is executed on a
resource multiple times with different input arguments, it can be represented
succinctly.  Similarly, when a resource attribute is changed it only has to be
changed in one place for every series that references it to be updated.
Initial Inca configuration and maintenance is therefore easier and less error prone.

@@

To further manage the Inca deployment, the agent regularly pings the reporter
managers on each resource in order to detect when a reporter manager has
failed so it can be restarted.  For example, if a resource goes down for a
planned maintenance, the agent will attempt to restart the reporter manager
(by default every hour) until it succeeds.  The agent also maintains a local
cache of reporters and their dependencies; it periodically checks the
repositories for updates (every 4 hours by default) and automatically
distributes them to the reporter managers if the latest version is desired.  
The agent is implemented using Java.

@@

The reporter manager is implemented using Perl because Perl is available by default
on UNIX machines.  The cron scheduling is implemented using the CPAN Perl
module Schedule::Cron.

@@

The Inca depot server is responsible for storing configuration information and
the data produced by reporters. The depot uses a relational database via
Hibernate~\cite{hibernate} enabling the use of a variety of database backends.  The depot provides full archiving of reporter output and structures its schema
around series and the minimization of redundant data, i.e., only stores
changes from one report to another in a report series.  The depot also
supports comparisons that are executed on a newly received report; 
% need Jim's help with this sentence
currently regular expression matching and greater than/less than comparisons are 
supported.  Optionally, an Inca administrator can select to receive
email notification when the result of the comparison changes.

Data can be queried using SQL queries. Predefined queries exist to return the
latest report instances of a suite, a single report instance, or a report
history.  A Web services interface is also available to provide
unauthenticated query access to data.  The depot is implemented using Java.
